\documentclass[main.tex]{subfiles}

\begin{document}

\section{Introduction}
The aim of the project is to study the variable length 
pendulum (VLP) presented in \cite{xin2014control} along
with the controllers designed to make it achieve a 
desired swing motion given a desired energy and a desired
length of the pendulum.

The report introduces the theory needed to
study the stability of the considered systems in Section
\ref{sec:theoretical-background}, describing invariant
sets and LaSalle's invariance principle. A detailed
description of the variable length pendulum is given in
Section \ref{sec:motion-equation}, where the dynamics
equations of the VLP are introduced by using Euler-Lagrange
equations. The trajectory control problem is briefly
described in Section \ref{sec:problem-formulation}.
Section \ref{sec:controller-design} studies two approaches
to design the controllers that make the VLP perform a
swing trajectory. The first one is based on total energy
shaping while the second one is based on partial energy shaping.
Section \ref{sec:motion-analysis} analyzes the behaviour
of the VLP under the controller designed with partial
energy shaping, discussing the stability of the
equilibrium points of the system. Section
\ref{sec:simulation-results} presents a few simulation
experiments which have been performed through a custom
Simulink implementation of the controllers studied in
this report. Section \ref{sec:conclusion} concludes
the report, summarizing the obtained results.

\end{document}